---
title: "Array miRNA mouse"
author: "Silveyra"
date: "May 4 2017"
output:
  html_document: default
---

```{r}
source("https://bioconductor.org/biocLite.R")
biocLite()
biocLite("limma")
biocLite("hexbin")
biocLite("affy")
biocLite("gage")
library(gage)

```

```{r}
require(hexbin)
require(limma)
require(affy)
require(gplots)
require(RColorBrewer)
```



```{r}
setwd("~/Dropbox/miRNA arrays to upload in R")
CTvalues=read.csv("array2noH.csv")
pheno=read.csv("miRNAmatrix.csv")
pheno2=read.csv("miRNAmatrix2.csv")
pheno2M=read.csv("miRNAmatrix2M.csv")
pheno2F=read.csv("miRNAmatrix2F.csv")
pheno2FP=read.csv("miRNAmatrix2FP.csv")
pheno2FnoP=read.csv("miRNAmatrix2FnoP.csv")
pheno3=read.csv("miRNAmatrix3.csv")
phenoFA=read.csv("miRNAmatrixFA.csv")
phenoO3=read.csv("miRNAmatrixO3.csv")
samplenames=c(pheno$Sample)
samplenames2=c(pheno2$Sample)
samplenames3=c(pheno3$Sample)
samplenamesFA=c(phenoFA$Sample)
samplenamesO3=c(phenoO3$Sample)
samplenamesM=c(pheno2M$Sample)
samplenamesF=c(pheno2F$Sample)
samplenamesFP=c(pheno2FP$Sample)
samplenamesFnoP=c(pheno2FnoP$Sample)
datawithID=read.csv("array2.csv")
miRNAlist=datawithID[,1]
miRNAlist=data.matrix(miRNAlist)
colnames(CTvalues)=samplenames
```

{r summary and plots of Ct raw data}
CTvaluesM=data.matrix(CTvalues)
boxplot(CTvaluesM)
summary(CTvaluesM)
plotCtHeatmap(CTvaluesM, gene.names = miRNAlist, sample.names = pheno$Treatment, dist = "euclidean", "CT all cycles")
plotCtHeatmap(CTvaluesM, gene.names = miRNAlist, dist = "euclidean", "CT all 

```{r groups}
FA=c(1,2,5,6,17,18,11,40,41,42,43,50,28,52,10,14,23,27,38,49,54,55,56,25,29,37,44,45,47)
O3=c(3,4,7,8,9,19,20,21,24,33,51,34,39,53,16,22,26,30,31,32,36,46,48,12,13,15,35)
pheno$Treatment[FA]
pheno$Treatment[O3]

FA_M=c(1,2,5,6,17,18)
pheno$code[FA_M]
O3_M=c(3,4,7,8,9,19,20,21)
pheno$code[O3_M]

FA_F=c(11,40,41,42,43,50,28,52,10,14,23,27,38,49,54,55,56,25,29,37,44,45,47)
pheno$code[FA_F]
O3_F=c(24,33,51,34,39,53,16,22,26,30,31,32,36,46,48,12,13,15,35)
pheno$code[O3_F]


FA_D1=c(11,40,42,43)
pheno$code2[FA_D1]
FA_D2=c(28,41,50,52)
pheno$code2[FA_D2]
FA_luteal=c(11,40,41,42,43,50,28,52)
pheno$Phase[FA_luteal]
FA_noP=c(11,40,41,42,43,50,28,52,25,29,37,44,45,47)
pheno$code3[FA_noP]

FA_P=c(10,14,23,27,38,49,54,55,56)
pheno$code2[FA_P]
FA_E=c(25,29,37,44,45,47)
pheno$code2[FA_E]
FA_follicular=c(10,14,23,27,38,49,54,55,56,25,29,37,44,45,47)
pheno$Phase[FA_follicular]


O3_D1=c(24,33,51)
pheno$code2[O3_D1]
O3_D2=c(34,39,53)
pheno$code2[O3_D2]
O3_luteal=c(24,33,51,34,39,53)
pheno$Phase[O3_luteal]
O3_noP=c(24,33,51,34,39,53,12,13,15,35)
pheno$code3[O3_noP]

O3_P=c(16,22,26,30,31,32,36,46,48)
pheno$code2[O3_P]
O3_E=c(12,13,15,35)
pheno$code2[O3_E]
O3_follicular=c(16,22,26,30,31,32,36,46,48,12,13,15,35)
pheno$Phase[O3_follicular]
```

```{r}
plot(hexplom(CTvaluesM[,FA_M]), main = "FA M")
plot(hexplom(CTvaluesM[,O3_M]), main = "O3 M")

plot(hexplom(CTvaluesM[,FA_F]), main = "FA F")
plot(hexplom(CTvaluesM[,O3_F]), main = "O3 F")

plot(hexplom(CTvaluesM[,FA_D1]), main = "FA D1")
plot(hexplom(CTvaluesM[,O3_D1]), main = "O3 D1")

plot(hexplom(CTvaluesM[,FA_D2]), main = "FA D2")
plot(hexplom(CTvaluesM[,O3_D2]), main = "O3 D2")

plot(hexplom(CTvaluesM[,FA_P]), main = "FA P")
plot(hexplom(CTvaluesM[,O3_P]), main = "O3 P")

plot(hexplom(CTvaluesM[,FA_E]), main = "FA E")
plot(hexplom(CTvaluesM[,O3_E]), main = "O3 E")

plot(hexplom(CTvaluesM[,FA_follicular]), main = "FA folLicular")
plot(hexplom(CTvaluesM[,O3_follicular]), main = "O3 folLicular")

plot(hexplom(CTvaluesM[,FA_luteal]), main = "FA luteal")
plot(hexplom(CTvaluesM[,O3_luteal]), main = "O3 luteal")
```

```{r}
Expvalues=read.csv("expression1noH.csv")
colnames(Expvalues)=samplenames
datawithID2=read.csv("expression1.csv")
miRNAlist2=datawithID2[,1]
rownames(Expvalues)=miRNAlist2
ExpvaluesM=data.matrix(Expvalues)
ExpvaluesL=log(ExpvaluesM)
```

```{r}
Expvalues2=read.csv("expression1noH2.csv")
colnames(Expvalues2)=samplenames2
datawithID22=read.csv("expression1.csv")
miRNAlist22=datawithID22[,1]
rownames(Expvalues2)=miRNAlist22
ExpvaluesM2=data.matrix(Expvalues2)
ExpvaluesL2=log(ExpvaluesM2)
```

```{r}
Expvalues3=read.csv("expression1noH23.csv")
colnames(Expvalues3)=samplenames3
datawithID23=read.csv("expression123.csv")
miRNAlist23=datawithID23[,1]
rownames(Expvalues3)=miRNAlist23
ExpvaluesM3=data.matrix(Expvalues3)
ExpvaluesL3=log(ExpvaluesM3)
```

```{r}
ExpvaluesFA=read.csv("expressionFAnoH.csv")
colnames(ExpvaluesFA)=samplenamesFA
rownames(ExpvaluesFA)=miRNAlist23
ExpvaluesFA=data.matrix(ExpvaluesFA)
ExpvaluesFAL=log(ExpvaluesFA)
```

```{r}
ExpvaluesO3=read.csv("expressionO3noH.csv")
colnames(ExpvaluesO3)=samplenamesO3
rownames(ExpvaluesO3)=miRNAlist23
ExpvaluesO3=data.matrix(ExpvaluesO3)
ExpvaluesO3L=log(ExpvaluesO3)
```

```{r}
ExpvaluesMale=read.csv("expressionMalenoH.csv")
colnames(ExpvaluesMale)=samplenamesM
rownames(ExpvaluesMale)=miRNAlist23
ExpvaluesMale=data.matrix(ExpvaluesMale)
```

```{r}
ExpvaluesF=read.csv("expressionFnoH.csv")
colnames(ExpvaluesF)=samplenamesF
rownames(ExpvaluesF)=miRNAlist23
ExpvaluesF=data.matrix(ExpvaluesF)
```

```{r}
ExpvaluesFP=read.csv("expressionFPnoH.csv")
colnames(ExpvaluesFP)=samplenamesFP
rownames(ExpvaluesFP)=miRNAlist23
ExpvaluesFP=data.matrix(ExpvaluesFP)
```

```{r}
ExpvaluesFnoP=read.csv("expressionFnoPnoH.csv")
colnames(ExpvaluesFnoP)=samplenamesFnoP
rownames(ExpvaluesFnoP)=miRNAlist23
ExpvaluesFnoP=data.matrix(ExpvaluesFnoP)

ExpvaluesFnoPsel=read.csv("expressionFnoPselnoH.csv")
datawithIDnoPsel=read.csv("expressionFnoPsel.csv")
miRNAlistnoPsel=datawithIDnoPsel[,1]
rownames(ExpvaluesFnoPsel)=miRNAlistnoPsel
colnames(ExpvaluesFnoPsel)=samplenamesFnoP
rownames(ExpvaluesFnoPsel)=miRNAlistnoPsel
ExpvaluesFnoPsel=data.matrix(ExpvaluesFnoPsel)

ExpvaluesFPsel=read.csv("expressionFPselnoH.csv")
datawithIDPsel=read.csv("expressionFPsel.csv")
miRNAlistPsel=datawithIDPsel[,1]
rownames(ExpvaluesFPsel)=miRNAlistPsel
colnames(ExpvaluesFPsel)=samplenamesFP
rownames(ExpvaluesFPsel)=miRNAlistPsel
ExpvaluesFPsel=data.matrix(ExpvaluesFPsel)
```

```{r visualize expression data}
boxplot(Expvalues, main = "raw expression")
boxplot(Expvalues[,FA], main = "FA")
boxplot(Expvalues[,O3], main = "O3")
boxplot(Expvalues[,FA_M], main = "FA M")
boxplot(Expvalues[,O3_M], main = "O3 M")
boxplot(Expvalues[,FA_F], main = "FA F")
boxplot(Expvalues[,O3_F], main = "O3 F")
```



```{r}
design=model.matrix(~0 + pheno$Treatment)
colnames(design)=c("FA", "O3")
rownames(design)=pheno$Sample
print(design)
```

```{r}
design1=model.matrix(~0 + pheno$code)
colnames(design1)=c("FA_F", "FA_M", "O3_F", "O3_M")
rownames(design1)=pheno$Sample
print(design1)
```

```{r}
design2=model.matrix(~0 + pheno$code2)
colnames(design2)=c("FA_D1", "FA_D2","FA_P", "FA_M", "FA_E", "O3_D1", "O3_D2", "O3_P", "O3_M",  "O3_E")
rownames(design2)=pheno$Sample
print(design2)
```

```{r}
design3=model.matrix(~0 + pheno$Phase)
colnames(design3)=c("FA_follicular", "FA_luteal", "FA_male",  "O3_follicular", "O3_luteal", "O3_male")
rownames(design3)=pheno$Sample
print(design3)
```

```{r}
design4=model.matrix(~0 + pheno$code3)
colnames(design4)=c("FA_M","FA_noP", "FA_P","O3_M","O3_noP","O3_P")
rownames(design4)=pheno$Sample
print(design4)
```


CONTRASTS

```{r contrasts}
contrasts=makeContrasts(O3vFA=O3-FA,levels = design)
contrasts1=makeContrasts(MvF_FA=FA_F-FA_M, MvF_O3=O3_F-O3_M,levels = design1)
contrasts2=makeContrasts(FAvO3_M=O3_M-FA_M, FAvO3_F=O3_F-FA_F, levels = design1)
contrasts3=makeContrasts(FAvO3_fol=O3_follicular-FA_follicular, FAvO3_lut=O3_luteal-FA_luteal, FAvO3_male=O3_male-FA_male, O3_folvslut=O3_luteal-O3_follicular, FA_folvslut=FA_luteal-FA_follicular, levels = design3)
contrasts4=makeContrasts(FAvO3noP=O3_noP-FA_noP,FAvO3P=O3_P-FA_P, levels = design4)
print(contrasts)
print(contrasts1)
print(contrasts2)
print(contrasts3)
print(contrasts4)
```


```{r}
fit=lmFit(Expvalues,design)
fit1=lmFit(Expvalues,design1)
fit3=lmFit(Expvalues,design3)
fit2=lmFit(Expvalues,design2)
fit4=lmFit(Expvalues,design4)

fitL=lmFit(ExpvaluesL,design)
fit1L=lmFit(ExpvaluesL,design1)
fit3L=lmFit(ExpvaluesL,design3)
fit2L=lmFit(ExpvaluesL,design2)
fit4L=lmFit(ExpvaluesL,design4)
```

```{r fit cell means with contrasts}
fitcontrast=contrasts.fit(fit,contrasts)
efitcontrast=eBayes(fitcontrast)

fitcontrast1=contrasts.fit(fit1,contrasts1)
efitcontrast1=eBayes(fitcontrast1)

fitcontrast2=contrasts.fit(fit1,contrasts2)
efitcontrast2=eBayes(fitcontrast2)

fitcontrast3=contrasts.fit(fit3,contrasts3)
efitcontrast3=eBayes(fitcontrast3)

fitcontrast4=contrasts.fit(fit4,contrasts4)
efitcontrast4=eBayes(fitcontrast4)

fitcontrastL=contrasts.fit(fitL,contrasts)
efitcontrastL=eBayes(fitcontrastL)

fitcontrast1L=contrasts.fit(fit1L,contrasts1)
efitcontrast1L=eBayes(fitcontrast1L)

fitcontrast2L=contrasts.fit(fit1L,contrasts2)
efitcontrast2L=eBayes(fitcontrast2L)

fitcontrast3L=contrasts.fit(fit3L,contrasts3)
efitcontrast3L=eBayes(fitcontrast3L)

fitcontrast4L=contrasts.fit(fit4L,contrasts4)
efitcontrast4L=eBayes(fitcontrast4L)
```






FA vs O3 top table

```{r}
FAvO3top=topTable(efitcontrast, coef = "O3vFA", adjust.method = "BH", p.value = 0.2, sort.by = "P")
FAvO3top
write.csv(FAvO3top, file = "O3vFA.csv")


FAvO3top2=topTable(efitcontrast, coef = "O3vFA", n=7)
FAvO3top2
write.csv(FAvO3top2, file = "O3vFAall.csv")

FAvO3topt=topTable(efitcontrast, coef = "O3vFA")
FAvO3topt
```



male vs female FA top tables

```{r}
MvF_FA_top=topTable(efitcontrast1, coef = "MvF_FA", adjust.method = "BH", p.value = 0.2, sort.by = "P")
MvF_FA_top

MvF_FA_top2=topTable(efitcontrast1, coef = "MvF_FA", n=3)
MvF_FA_top2
write.csv(MvF_FA_top2, file = "MvF_FAall.csv")
```


male vs female O3 top tables 

```{r}
MvF_O3_top=topTable(efitcontrast1, coef = "MvF_O3", adjust.method = "BH", p.value = 0.2, sort.by = "P")
MvF_O3_top
write.csv(MvF_O3_top, file = "MvF_O3.csv")

MvF_O3_top2=topTable(efitcontrast1, coef = "MvF_O3", n=20)
MvF_O3_top2
write.csv(MvF_O3_top2, file = "MvF_O3all.csv")
```

Graphs FOR FIGURES

FIGURE 1



ARRAY

```{r}
codeFA=phenoFA$sex
codeFA2=phenoFA$code2
colnames(ExpvaluesFA)=codeFA2
par(mfrow=c(1,1))
aheatmap(ExpvaluesFA, color = colorRampPalette(c("navy", "white", "firebrick3"))(50), scale="row", annColors = "Set2", Colv = NA, Rowv=NA, annLegend = TRUE, annCol = codeFA)
```

```{r}
codeO3=phenoO3$sex
codeO32=phenoO3$code2
colnames(ExpvaluesO3)=codeO32
par(mfrow=c(1,1))
aheatmap(ExpvaluesO3, color = colorRampPalette(c("navy", "white", "firebrick3"))(50), scale="row", annColors = "Set2", Colv = NA, Rowv=NA, annLegend = TRUE, annCol = codeO3)
```

```{r}
par(mfrow=c(2,3))
boxplot(ExpvaluesFA[66,] ~ phenoFA$code, main = miRNAlist2[66], ylab = "expression", xlab ="p=0.031")
boxplot(ExpvaluesFA[36,] ~ phenoFA$code, main = miRNAlist2[36], ylab = "expression", xlab ="p=0.047")
```


```{r}
par(mfrow=c(2,3))
boxplot(ExpvaluesO3[9,] ~ phenoO3$code, main = miRNAlist2[9], ylab = "expression",  xlab ="p=0.0004")
boxplot(ExpvaluesO3[58,] ~ phenoO3$code, main = miRNAlist2[58], ylab = "expression", xlab ="p=0.0014")
boxplot(ExpvaluesO3[14,] ~ phenoO3$code, main = miRNAlist2[14], ylab = "expression", xlab ="p=0.0023")
boxplot(ExpvaluesO3[40,] ~ phenoO3$code, main = miRNAlist2[40], ylab = "expression", xlab ="p=0.0057")
boxplot(ExpvaluesO3[23,] ~ phenoO3$code, main = miRNAlist2[23], ylab = "expression", xlab ="p=0.0096")
boxplot(ExpvaluesO3[17,] ~ phenoO3$code, main = miRNAlist2[17], ylab = "expression", xlab ="p=0.0132")
boxplot(ExpvaluesO3[55,] ~ phenoO3$code, main = miRNAlist2[55], ylab = "expression", xlab ="p=0.0151")
boxplot(ExpvaluesO3[44,] ~ phenoO3$code, main = miRNAlist2[44], ylab = "expression", xlab ="p=0.0153")
boxplot(ExpvaluesO3[22,] ~ phenoO3$code, main = miRNAlist2[22], ylab = "expression", xlab ="p=0.023")
```


males

```{r}
par(mfrow=c(2,2))
boxplot(ExpvaluesMale[36,] ~ pheno2M$code, main = miRNAlist2[36], ylab = "expression",  xlab ="p=0.011")
boxplot(ExpvaluesMale[58,] ~ pheno2M$code, main = miRNAlist2[58], ylab = "expression",  xlab ="p=0.015")
boxplot(ExpvaluesMale[29,] ~ pheno2M$code, main = miRNAlist2[29], ylab = "expression",  xlab ="p=0.021")
boxplot(ExpvaluesMale[72,] ~ pheno2M$code, main = miRNAlist2[72], ylab = "expression",  xlab ="p=0.029")
boxplot(ExpvaluesMale[8,] ~ pheno2M$code, main = miRNAlist2[8], ylab = "expression",  xlab ="p=0.031")
boxplot(ExpvaluesMale[14,] ~ pheno2M$code, main = miRNAlist2[14], ylab = "expression",  xlab ="p=0.037")
boxplot(ExpvaluesMale[17,] ~ pheno2M$code, main = miRNAlist2[17], ylab = "expression",  xlab ="p=0.045")
boxplot(ExpvaluesMale[9,] ~ pheno2M$code, main = miRNAlist2[9], ylab = "expression",  xlab ="p=0.049")
```


females

```{r}
par(mfrow=c(2,2))
boxplot(ExpvaluesF[72,] ~ pheno2F$code, main = miRNAlist2[72], ylab = "expression",  xlab ="p=0.002")
boxplot(ExpvaluesF[71,] ~ pheno2F$code, main = miRNAlist2[71], ylab = "expression",  xlab ="p=0.009")
boxplot(ExpvaluesF[50,] ~ pheno2F$code, main = miRNAlist2[50], ylab = "expression",  xlab ="p=0.014")
boxplot(ExpvaluesF[73,] ~ pheno2F$code, main = miRNAlist2[73], ylab = "expression",  xlab ="p=0.017")
boxplot(ExpvaluesF[62,] ~ pheno2F$code, main = miRNAlist2[62], ylab = "expression",  xlab ="p=0.035")
boxplot(ExpvaluesF[69,] ~ pheno2F$code, main = miRNAlist2[69], ylab = "expression",  xlab ="p=0.036")
boxplot(ExpvaluesF[9,] ~ pheno2F$code, main = miRNAlist2[9], ylab = "expression",  xlab ="p=0.041")
boxplot(ExpvaluesF[55,] ~ pheno2F$code, main = miRNAlist2[55], ylab = "expression",  xlab ="p=0.044")
```


NO P

```{r}
par(mfrow=c(2,3))
boxplot(ExpvaluesFnoP[38,] ~ pheno2FnoP$code, main = miRNAlist2[38], ylab = "expression", xlab ="p=0.027")
boxplot(ExpvaluesFnoP[54,] ~ pheno2FnoP$code, main = miRNAlist2[54], ylab = "expression", xlab ="p=0.039")
```

P

```{r}
par(mfrow=c(2,3))
boxplot(ExpvaluesFP[71,] ~ pheno2FP$code2, main = miRNAlist2[71], ylab = "expression", xlab ="p=0.00015")
boxplot(ExpvaluesFP[73,] ~ pheno2FP$code2, main = miRNAlist2[73], ylab = "expression", xlab ="p=0.00025")
boxplot(ExpvaluesFP[35,] ~ pheno2FP$code2, main = miRNAlist2[35], ylab = "expression", xlab ="p=0.003")
boxplot(ExpvaluesFP[26,] ~ pheno2FP$code2, main = miRNAlist2[26], ylab = "expression", xlab ="p=0.0055")
boxplot(ExpvaluesFP[75,] ~ pheno2FP$code2, main = miRNAlist2[75], ylab = "expression", xlab ="p=0.0092")
boxplot(ExpvaluesFP[72,] ~ pheno2FP$code2, main = miRNAlist2[72], ylab = "expression", xlab ="p=0.013")
boxplot(ExpvaluesFP[9,] ~ pheno2FP$code2, main = miRNAlist2[9], ylab = "expression", xlab ="p=0.019")
boxplot(ExpvaluesFP[32,] ~ pheno2FP$code2, main = miRNAlist2[32], ylab = "expression", xlab ="p=0.023")
boxplot(ExpvaluesFP[11,] ~ pheno2FP$code2, main = miRNAlist2[11], ylab = "expression", xlab ="p=0.038")
```



FA vs O3 males  

```{r}
FAvO3_M_top=topTable(efitcontrast2, coef = "FAvO3_M", adjust.method = "BH", p.value = 0.2, sort.by = "P")
FAvO3_M_top
write.csv(FAvO3_M_top, file = "FAvO3_M.csv")

FAvO3_M_top2=topTable(efitcontrast2, coef = "FAvO3_M", n=15)
FAvO3_M_top2
write.csv(FAvO3_M_top2, file = "FAvO3_Mall.csv")
```

FA vs O3 females 

```{r}
FAvO3_F_top=topTable(efitcontrast2, coef = "FAvO3_F", adjust.method = "BH", p.value = 0.2, sort.by = "P")
FAvO3_F_top
write.csv(FAvO3_F_top, file = "FAvO3_F.csv")

FAvO3_F_top2=topTable(efitcontrast2, coef = "FAvO3_F", n=9)
FAvO3_F_top2
write.csv(FAvO3_F_top2, file = "FAvO3_Fall.csv")
```


```{r}
boxplot(ExpvaluesM[9,] ~ pheno$code, main = miRNAlist2[9], ylab = "expression")
```



FA vs O3 in follicular and luteal phase

```{r}
topfolO3FA=toptable(efitcontrast3, coef = "FAvO3_fol", adjust.method = "BH", p.value = 0.2, sort.by = "P")
topfolO3FA

topfolO3FA2=toptable(efitcontrast3, coef = "FAvO3_fol", n=4)
topfolO3FA2

write.csv(topfolO3FA2, file = "topfolO3FAall.csv")



toplutO3FA=toptable(efitcontrast3, coef = "FAvO3_lut", adjust.method = "BH", p.value = 0.2, sort.by = "P")
toplutO3FA

toplutO3FA2=toptable(efitcontrast3, coef = "FAvO3_lut",n=6)
toplutO3FA2

write.csv(toplutO3FA2, file = "toplutO3FAall.csv")



topmaleO3FA=toptable(efitcontrast3, coef = "FAvO3_male", adjust.method = "BH", p.value = 0.2, sort.by = "P")
topmaleO3FA

topmaleO3FA2=toptable(efitcontrast3, coef = "FAvO3_male",n=14)
topmaleO3FA2

write.csv(topmaleO3FA2, file = "topmaleO3FAall.csv")
```


FA vs O3 in PROESTRUS

```{r}
topFAvO3noP=toptable(efitcontrast4, coef = "FAvO3noP", adjust.method = "BH", p.value = 0.5, sort.by = "P")
topFAvO3noP

write.csv(topFAvO3noP, file = "topFAvO3noP.csv")

topFAvO3P=toptable(efitcontrast4, coef = "FAvO3P", adjust.method = "BH", p.value = 0.5, sort.by = "P")
topFAvO3P
write.csv(topFAvO3P, file = "topFAvO3P.csv")
```

raw expression FA vs ozone luteal phase

```{r}
boxplot(ExpvaluesL[71,] ~ pheno$code3, main = miRNAlist2[71], ylab = "expression")
```



Follicular vs. Luteal phase 

```{r}
topfollutO3=toptable(efitcontrast3, coef = "O3_folvslut", adjust.method = "BH", p.value = 0.2, sort.by = "P")
topfollutO3

topfollutO32=toptable(efitcontrast3, coef = "O3_folvslut", n=8)
topfollutO32

write.csv(topfollutO32, file = "topfollutO3all.csv")


topfollutFA=toptable(efitcontrast3, coef = "FA_folvslut", adjust.method = "BH", p.value = 0.2, sort.by = "P")
topfollutFA

topfollutFA2=toptable(efitcontrast3, coef = "FA_folvslut", n=2)
topfollutFA2

write.csv(topfollutO32, file = "topfollutFAall.csv")

```

```{r}
boxplot(ExpvaluesM[72,] ~ pheno$Phase, main = miRNAlist2[72], ylab = "expression")
boxplot(ExpvaluesM[35,] ~ pheno$code, main = miRNAlist2[35], ylab = "expression")
boxplot(ExpvaluesM[72,] ~ pheno$Treatment, main = miRNAlist2[72], ylab = "expression")
```


```{r}
heatmap(ExpvaluesM,labRow = miRNAlist2, labCol = pheno$Treatment)
heatmap(ExpvaluesM,labRow = miRNAlist2, labCol = pheno$code)
heatmap(ExpvaluesM,labRow = miRNAlist2, labCol = pheno$Phase)
heatmap(ExpvaluesM,labRow = miRNAlist2, labCol = pheno$code2)
```

```{r}
heatmap(ExpvaluesL,labRow = miRNAlist2, labCol = pheno$Treatment)
heatmap(ExpvaluesL,labRow = miRNAlist2, labCol = pheno$code)
heatmap(ExpvaluesL,labRow = miRNAlist2, labCol = pheno$Phase)
heatmap(ExpvaluesL,labRow = miRNAlist2, labCol = pheno$code2)
```


```{r}
d1=dist(ExpvaluesM2, method = "euclidean", diag = FALSE, upper = FALSE)
c1=hclust(d1, method = "ward.D2", members = NULL)
ExpvaluesM2t=t(ExpvaluesM2)
d2=dist(ExpvaluesM2t,method = "euclidean", diag = FALSE, upper = TRUE)
c2=hclust(d2, method = "ward.D2", members = NULL)
par(mfrow=c(2,1),cex=0.5)
plot(c2); plot(c1) 
my_palette <- colorRampPalette(c("blue","white","red"))(n = 50)
par(cex.main=0.75)
heatmap.2(ExpvaluesM2,trace="none", col=my_palette, labCol = pheno2$code, scale="row", Colv = NA)
```

```{r}
if (!require("NMF")) {
   install.packages("NMF", dependencies = TRUE)
   library(NMF)
}
```


```{r}
codes=pheno2$code
codes2=pheno2$code2
colnames(ExpvaluesL2)=codes2
par(mfrow=c(1,1))
aheatmap(ExpvaluesL2[,1:14], color = colorRampPalette(c("navy", "white", "firebrick3"))(50), scale="row", annColors = "Set3", Colv = NA, Rowv=NA, annLegend = TRUE, annCol = pheno2$Treatment[1:14], border = T)
aheatmap(ExpvaluesL2[,15:54], color = colorRampPalette(c("navy", "white", "firebrick3"))(50), scale="row", annColors = "Set3", Colv = NA, Rowv=NA, annCol = pheno2$Treatment[15:54], cexRow = 1, border = T)
```

color = rev(brewer.pal(9,"RdBu"))

```{r}
par(mfrow=c(1,1))
codes3=pheno3$code2
colnames(ExpvaluesL3)=codes3
myt = data.frame(Treatment = pheno3$Treatment, Cycle = pheno3$Cycle)
aheatmap(ExpvaluesL3, color = colorRampPalette(c("navy", "white", "firebrick"))(50), scale="row", Colv = NA, Rowv=NA, annCol = myt, border = T)
```


```{r}
par(mfrow=c(1,1))
codesFP=pheno2FP$code2
colnames(ExpvaluesFPsel)=codesFP
myt = data.frame(Treatment = pheno2FP$Treatment)
aheatmap(ExpvaluesFPsel, color = colorRampPalette(c("navy", "white", "firebrick"))(50), scale="row", Colv = NA, Rowv=NA, annCol = myt,border = T)

codesFnoP=pheno2FnoP$code2
colnames(ExpvaluesFnoPsel)=codesFnoP
myt = data.frame(Treatment = pheno2FnoP$Treatment)
aheatmap(ExpvaluesFnoPsel, color = colorRampPalette(c("navy", "white", "firebrick3"))(50), scale="row", Colv = NA, Rowv=NA, annCol = myt, border = T)
```


aheatmap(ExpvaluesL3, color = rev(brewer.pal(9,"RdBu")), scale="row", annColors = "Set2", Colv = NA, Rowv=NA, annCol = pheno3$Cycle)

```{r}
heatmap.2(ExpvaluesFPsel,labRow = miRNAlistPsel, labCol = pheno2F$code2, scale="row", density.info="none", trace="none", col=brewer.pal(11,"RdBu"))
```

```{r}
heatmap(ExpvaluesFPsel,labRow = miRNAlistPsel, labCol = pheno3$Treatment)
heatmap(ExpvaluesL3,labRow = miRNAlist23, labCol = pheno3$code2)
```



```{r}
sessionInfo()
print(gc())
```












